\documentclass{muratcan_cv}
\setname{John}{Wohlbier}
\setaddress{Washington, DC USA}
\setmobile{(505) 412-0128}
\setmail{jgwohlbier@sei.cmu.edu}
\setposition{Senior Research Scientist} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/john-wohlbier-52a6b5a1/}
\setgithubaccount{https://github.com/wohlbier}
\setthemecolor{red}

\begin{document}
\headerview
\vspace{1ex}

% Summary
\addblocktext{Summary}{%
  Dr.~Wohlbier does computing.
}

%Education
\section{Education}
\datedexperience{University of Wisconsin}{}
\explanation{Doctor of Philosophy in Electrical and Computer
  Engineering -- 2003}
\explanationdetail{{\bf Thesis --} Nonlinear Distortion and
  Suppression in Traveling Wave Tubes: Insights and Methods.}
\explanation{Master of Science in Electrical and Computer
  Engineering -- 2000}
\explanationdetail{{\bf Thesis --} Modeling and Analysis of a
  Traveling Wave Tube Under Multitone Excitation.}
\explanation{Bachelor of Science in Electrical and Computer
  Engineering  -- 1993}

%    \explanationdetail{\coloredbullet\ %
%     }

% Experience
\section{Experience}
\datedexperience{Carnegie Mellon University -- Software
  Engineering Institute -- Emerging Technology Center}{2018 -- present}
\explanation{Senior Research Scientist}
\explanationdetail{}

\vspace{1ex}
\datedexperience{Engility Corportation}{2016 -- 2018}
\explanation{Computational Scientist}
\explanationdetail{Performance engineering for US Navy computational
  fluid dynamics codes. Application of performance analysis tools
  including Allinea MAP, Open$|$SpeedShop, Scalasca, Score-p, TAU, and
  Ravel to diagnose performance issues and implement solutions to
  improve performance. Developed best practices guide for application
  of performance engineering methodologies to scientific codes. Worked
  on performance engineering of computational fluid dynamics miniapps
  on Intel Knight's Landing processors.}

\vspace{1ex}
\datedexperience{Los Alamos National Laboratory}{2005 -- 2016}
\explanation{Computational Scientist}
\explanationdetail{{\bf Multi-physics software development for high
    performance computing.} Active on several multi-physics code
  projects for high performance computing for 10 years. Physics
  include but are not limited to compressible hydrodynamics,
  radiation-matter coupling, and magnetohydrodynamics. Activities
  included coding and optimization for Intel Xeon Phi coprocessors and
  NVidia GPUs, and implementation of distributed memory parallel
  domain decomposition and parallel I/O for an unstructured
  tetrahedral mesh code. C++/C/Fortran. MPI/OpenMP/OpenCL/CUDA.\\
  {\bf Project lead for ``Multi-physics on multi-core''.} Lead
  successful effort to develop multi-physics code for the Cell
  processor in the Roadrunner supercomputer era. Roadrunner was a
  radically different heterogeneous architecture that required
  simultaneous use of the three very different types of processors on
  the system. The compute engine on the Cell processor was a short
  vector processor similar to what is emerging in current Intel
  hardware, but had additional barriers to use such as the need to
  specifically issue direct memory accesses (DMA's) to load
  registers.\\
  {\bf Data Science Consultant.} Consulted on several data science
  projects with data science company. Developed {\em R} based
  prediction models using large financial and demographic data
  sets. Name of data science company available upon request.\\
  {\bf Post-doc and graduate student mentor.} Mentored two
  post-doctoral researchers, both of which are now productive and well
  respected staff scientists. Mentored and worked with several
  graduate students pursuing degrees in computational physics.
}

\vspace{1ex}
\datedexperience{Los Alamos National Laboratory}{2003 -- 2005}
\explanation{Agnew National Security Post-doctoral Fellow, High
  Power Electrodynamics Group (ISR-6)}
\explanationdetail{}

\vspace{1ex}
\datedexperience{Department of Engineering Physics -- University of
  Wisconsin}{2003 -- 2003}
\explanation{Postdoctoral Researcher}
\explanationdetail{}

\section{Publications}
\begin{itemize}

\item Walden, A., Nielsen, E.J., Zubair, M., Linford, J.C., Wohlbier,
  J.G., Luitjens, J.P., Orender, J., Beekman, I., Khuvis, S. and Shende,
  S.S., 2017, November. Unstructured-Grid CFD Algorithms on Many-Core
  Architectures. In {\it Technical Research Posters of International
  Supercomputing Conference for High Performance Computing, Networking,
  Storage, and Analysis.} SC (Vol. 17).
\item Nystrom, W.D., Bergen, B., Bird, R.F., Bowers, K.J., Daughton,
  W.S., Guo, F., Li, H., Nam, H.A., Pang, X., Rust III, W.N. and
  Wohlbier, J., 2016. Performance of VPIC on Trinity. APS, 2016,
  pp.JP10-097.
\item Charest, M.R., Canfield, T.R., Morgan, N.R., Waltz, J. and
  Wohlbier, J.G., 2015. A high-order vertex-based central ENO
  finite-volume scheme for three-dimensional compressible
  flows. {\it Computers \& Fluids}, 114, pp.172-192.
\item Morgan, N.R., Waltz, J.I., Burton, D.E., Charest, M.R.,
  Canfield, T.R. and Wohlbier, J.G., 2015. A point-centered arbitrary
  Lagrangian Eulerian hydrodynamic approach for tetrahedral
  meshes. {\it Journal of Computational Physics}, 290, pp.239-273.
\item Waltz, J., Wohlbier, J.G., Risinger, L.D., Canfield, T.R.,
  Charest, M.R.J., Long, A.R. and Morgan, N.R., 2015. Performance
  analysis of a 3D unstructured mesh hydrodynamics code on multi‐core
  and many‐core architectures. {\it International Journal for Numerical
  Methods in Fluids}, 77(6), pp.319-333.
\item Morgan, N.R., Waltz, J.I., Burton, D.E., Charest, M.R.,
  Canfield, T.R. and Wohlbier, J.G., 2015. A Godunov-like
  point-centered essentially Lagrangian hydrodynamic approach. {\it Journal
  of Computational Physics}, 281, pp.614-652.
\item Waltz, J., Morgan, N.R., Canfield, T.R., Charest, M.R.J. and
  Wohlbier, J.G., 2014. A nodal Godunov method for Lagrangian shock
  hydrodynamics on unstructured tetrahedral grids. {\it International
  Journal for Numerical Methods in Fluids}, 76(3), pp.129-146.
\item Waltz, J., Canfield, T.R., Morgan, N.R., Risinger, L.D. and
  Wohlbier, J.G., 2014. Manufactured solutions for the
  three-dimensional Euler equations with relevance to Inertial
  Confinement Fusion. {\it Journal of Computational Physics}, 267,
  pp.196-209.
\item Waltz, J., Morgan, N.R., Canfield, T.R., Charest, M.R.,
  Risinger, L.D. and Wohlbier, J.G., 2014. A three-dimensional
  finite element arbitrary Lagrangian–Eulerian method for shock
  hydrodynamics on unstructured grids. {\it Computers \& Fluids}, 92,
  pp.172-187.
\item Waltz, J., Canfield, T.R., Morgan, N.R., Risinger, L.D. and
  Wohlbier, J.G., 2013. Verification of a three-dimensional
  unstructured finite element method using analytic and manufactured
  solutions. {\it Computers \& Fluids}, 81, pp.57-67.
\item Fatenejad, M., Fryxell, B., Wohlbier, J., Myra, E., Lamb, D.,
  Fryer, C. and Graziani, C., 2013. Collaborative comparison of
  simulation codes for high-energy-density physics applications. {\it High
  Energy Density Physics}, 9(1), pp.63-66.
\item Masser, T.O., Wohlbier, J.G. and Lowrie, R.B., 2011. Shock wave
  structure for a fully ionized plasma. {\it Shock waves}, 21(4),
  pp.367-381.
\item McClarren, R.G. and Wohlbier, J.G. Solutions for
  ion-electron-radiation coupling with radiation and electron
  diffusion. {\it J.~Quant.~Spectrosc.~Radiat.~Transfer}, 112, pp.119-130
  (2011).
\item Wohlbier, J.G., 2005. Phase distortion mechanisms in linear beam
  vacuum devices. {\it IEEE transactions on plasma science}, 33(3),
  pp.1031-1035.
\item Wöhlbier, J.G., Jin, S. and Sengele, S., 2005. Eulerian
  calculations of wave breaking and multivalued solutions in a
  traveling wave tube. {\it Physics of Plasmas}, 12(2), p.023106.
\item Wohlbier, J.G. and Booske, J.H., 2005. Nonlinear space charge
  wave theory of distortion in a klystron. {\it IEEE Transactions on
  Electron Devices}, 52(5), pp.734-741.
\item Singh, A., Scharer, J.E., Booske, J.H. and Wohlbier, J.G.,
  2005. Second-and third-order signal predistortion for nonlinear
  distortion suppression in a TWT. {\it IEEE Transactions on Electron
  Devices}, 52(5), pp.709-717.
\item Singh, A., Wohlbier, J.G., Booske, J.H. and Scharer, J.E.,
  2004. Experimental verification of the mechanisms for nonlinear
  harmonic growth and suppression by harmonic injection in a traveling
  wave tube. {\it Physical Review Letters}, 92(20), p.205005.
\item Li, X., Wöhlbier, J.G., Jin, S. and Booske, J.H., 2004. Eulerian
  method for computing multivalued solutions of the Euler-Poisson
  equations and applications to wave breaking in klystrons. {\it Physical
  Review E}, 70(1), p.016502.
\item Wöhlbier, J.G. and Booske, J.H., 2004. Mechanisms for phase
  distortion in a traveling wave tube. {\it Physical Review E}, 69(6),
  p.066502.
\item Wohlbier, J.G., Booske, J.H. and Dobson, I., 2004. On the
  physics of harmonic injection in a traveling wave tube. {\it IEEE
  Transactions on Plasma Science}, 32(3), pp.1073-1085.
\item Wohlbier, J.G., Dobson, I. and Booske, J.H., 2002. Generation
  and growth rates of nonlinear distortions in a traveling wave
  tube. {\it Physical Review E}, 66(5), p.056504.
\item Wohlbier, J.G., Booske, J.H. and Dobson, I., 2002. The
  multifrequency spectral Eulerian (MUSE) model of a traveling wave
  tube. {\it IEEE transactions on plasma science}, 30(3), pp.1063-1075.
\item Zhang, T., Wohlbier, J.G., Choquette, K.D. and Tabatabaie, N.,
  1995. Microcavity vacuum-field configuration and the spontaneous
  emission power. {\it IEEE Journal of Selected Topics in Quantum
  Electronics}, 1(2), pp.606-615.
\end{itemize}

%\noindent {\bf Synergystic Professional Activities}
%
%\begin{itemize}
%\item Leading {\ocl}~developement activity within \rage
%\item \rage\ code developer, Los Alamos National Laboratory. Develop
%multi-physics algorithms in the \rage\ code, including the initial
%implementation of a 3T model in \rage.\\
%\end{itemize}
%
%\noindent {\bf Collaborators and Other Affiliations}
%
%\noindent FLASH center (U.~Chicago), The \rage\ code team (LANL), R.B.~Lowrie
%(LANL), R.G.~McClarren (Texas A\&M), B.~Bergen (LANL), T.O.~Masser
%(LANL), M.~Calef (LANL).



%{\bf \large Research Experience}
%\begin{itemize}
%\item Technical Staff Member, Los Alamos National Laboratory,
%  Continuum Dynamics Group (CCS-2). 2005 -- present.\\
%  Develop code and numerical methods targeted for, but not limited to,
%  the \rage\ code. \rage\ is the LANL
%  flagship AMR Eulerian code for the Department of Energy's Advanced
%  Simulation and Computing (ASC) program:
%  \begin{itemize}
%  \item Developed the \xrage\ library, a set of \rage\ extensions for
%    linking advanced and alternate physics modules. \xrage\ highlights
%    include use of sophisticated parallel communication primitives to
%    enable large AMR stencils, and \rage\ interface to enable use of any
%    cell centered or vertex based hydro scheme. The \xrage\ interface
%    to \rage\ has been used to link to Paul Woodward's PPM-PPB
%    multi-fluid developmental hydro, a vertex based hydro algorithm
%    developed in LANL's X division, and \GPTe\ (below).
%  \item Developed \RL, a stand alone library of Riemann solvers for
%    hydrodyanmics applications. \RL\ is intended to grow to include a
%    large library of (possibly contributed) Riemann solvers.
%  \item Developed \GPTe, a stand alone library of pressure temperature
%    equilibrium Godunov hydrodyanmics solvers. \GPTe\ uses, but is not
%    limited to, \RL, and is
%    intended to grow to include a
%    large library of (possibly contributed) pressure temperature
%    equilibrium hydro solvers. \GPTe\ has been linked to \rage\
%    through the \xrage\ interface.
%  \item Performing research on multi-temperature hydro models for
%    implementation and eventual use in the \rage\ code.
%  \end{itemize}
%\end{itemize}

%{\bf\large Postdoctoral and Graduate Research Experience}
%\begin{itemize}
%\item Agnew National Security Postdoctoral Fellow, Los Alamos National
%  Laboratory, 2003--2005.
%  Applied novel analytic and numerical methods to study wave
%  breaking, saturation,
%  efficiency, and linearity in Traveling Wave Tubes and related
%  devices. Work was on forefront of methods in nonlinear
%  waves and shock physics.
%  %Large scale computations developed and
%  %performed on Los Alamos parallel computing resources.
%\item Postdoctoral Scholar, Nuclear Engineering and Engineering
%  Physics, University of Wisconsin--Madison, 2003.
%  Performed theoretical and numerical research in stabilization
%  of ballooning instabilities in 3-d plasmas for magnetic fusion
%  applications. Work towards a publication is ongoing.
%\item Research Assistant, Electrical and Computer Engineering,
%  University of Wisconsin--Madison, 1997--2003.
%  Performed research in nonlinear behavior of Traveling Wave Tube
%  amplifiers. Research included computer simulations and theoretical
%  analyses of Traveling Wave Tubes and related devices and resulted in
%  eight refereed journal articles.
%\item Research Assistant, Electrical and Computer Engineering,
%  University of Wisconsin--Madison, 1993--1994.
%  Performed and published research in semiconductor lasers.
%\end{itemize}

%{\bf\large Education}
%\begin{itemize}
%\item Ph.D. in Electrical and Computer Engineering, University
%  of Wisconsin--Madison, May 2003.
%  Thesis: Nonlinear Distortion and Suppression in Traveling Wave
%  Tubes: Insights and Methods. Advisors: John Booske and Ian Dobson.
%\item Master of Science in Electrical Engineering,
%  University of Wisconsin--Madison, May 2000.
%  Thesis: Modeling and Analysis of a Traveling Wave Tube Under Multitone
%  Excitation.
%\item Bachelor of Science in Electrical Engineering,
%  University of Wisconsin--Madison, August 1993.
%\end{itemize}

%\input{files/teaching}

%{\bf\large Industrial Experience}
%\begin{itemize}
%\item Engineer, Soft Switching Technologies, Middleton,
%  Wisconsin, 1994--1997.\\
%  Electrical and mechanical engineering design for start-up company.
%  Involved in all facets of design and production of power quality
%  products.
%\end{itemize}
%
%%\clearpage
%%\pagebreak
%\fancyhead[R]{John G.~W\"ohlbier}


%{\bf\large Principal Research Accomplishments}
%\begin{itemize}
%\item Collaborated with mathematicians (University of Wisconsin and Princeton
%  University) to apply new Eulerian methods of solving nonlinear partial
%  differential equations to microwave vacuum electronics devices. Solves
%  fifty year old problem in vacuum electronics and plasma physics.
%\item Formulated nonlinear space charge wave theory of distortion in
%  klystrons.
%\item Discovered and described fundamental physical mechanism of harmonic
%  injection in Traveling Wave Tube Amplifiers.
%\item Discovered and described fundamental physical mechanism of phase
%  distortion in Traveling Wave Tube Amplifiers.
%\item Derived and tested formulas for growth rates of nonlinear distortion
%  products in Traveling Wave Tube Amplifiers.
%\item Developed Traveling Wave Tube code for research and design of
%  Traveling Wave Tubes. Code internationally known and used. See
%  {\tt http://www.lmsuite.org}
%\end{itemize}

%{\bf\large Research Interests}
%\begin{itemize}
%\item Computational physics and large scale computing
%\item Plasma physics
%\item Microwave electronics
%\item Dynamical systems
%\item Applied mathematics
%\end{itemize}

%{\bf\large Submitted Manuscripts}
%\begin{enumerate}
%\end{enumerate}

%{\bf\large Refereed Journal Publications}
%\begin{enumerate}
%\item J.G. W\"ohlbier. Phase distortion mechanisms in linear beam
%  vacuum devices. {\it IEEE Trans.~Plasma Sci.}, Vol.~33, no.~3,
%  2005.
%  \\$\Rightarrow$0 citations.
%\item J.G.~W\"ohlbier, S.~Jin, S.~Sengele. Eulerian calculations of
%  wave breaking and multi-valued solutions in a traveling wave
%  tube. {\it Physics of Plasmas} {\bf 12}, 023106 (2005).
%  \\$\Rightarrow$1 citation.
%\item J.G. W\"ohlbier and J.H. Booske. Nonlinear space charge wave theory
%  of distortion in a klystron. {\it IEEE Trans.~Electron Devices,}
%  Vol.~52, no.~5, 2005.
%  \\$\Rightarrow$1 citation.
%\item A. Singh, J.E. Scharer, J.H. Booske, and J.G. W\"ohlbier.
%  Second and third-order signal injection for nonlinear
%  distortion suppression in a traveling wave tube. {\it IEEE
%    Trans.~Electron Devices,} Vol.~52, no.~5, 2005.
%  \\$\Rightarrow$0 citations.
%\item A. Singh, J.G. W\"ohlbier, J.H. Booske, and
%  J.E. Scharer. Experimental Verification of the Mechanisms for
%  Nonlinear Harmonic Growth and Suppression by Harmonic Injection in a
%  Traveling Wave Tube. {\it Phys.~Rev.~Lett.} 92, 205005 (2004).
%  \\$\Rightarrow$2 citations.
%\item X. Li, J.G. W\"ohlbier, S. Jin, and J.H. Booske.
%  Eulerian Method for Computing Multi-valued solutions of the Euler-Poisson
%  Equations and Application to Wave Breaking in Klystrons.
%  {\it Phys.~Rev.~E} 70, 016502 (2004).
%  \\$\Rightarrow$3 citations.
%\item J.G. W\"ohlbier and J.H. Booske.
%  Mechanisms of Phase Distortion in a Traveling Wave Tube.
%  {\it Phys.~Rev.~E} 69, 066502 (2004).
%  \\$\Rightarrow$3 citations.
%\item J.G. W\"ohlbier, J.H. Booske, and I. Dobson.
%  On the Physics of Harmonic Injection in a Traveling Wave Tube.
%  {\it IEEE Trans.~Plasma Sci.}, Vol.~32, No.~3, (2004).
%  \\$\Rightarrow$3 citations.
%\item J.G. W\"ohlbier, I. Dobson, and J.H. Booske.
%  Generation and growth rates of nonlinear distortions in a traveling
%  wave tube. {\it Phys.~Rev.~E} 66, 56504 (2002).
%  \\$\Rightarrow$6 citations.
%\item J.G. W\"ohlbier, J.H. Booske, and I. Dobson.
%  The Multifrequency Spectral Eulerian (MUSE) Model of a Traveling Wave
%  Tube. {\it IEEE Trans.~Plasma Sci.} Vol.~30, no.~3, June 2002.
%  \\$\Rightarrow$11 citations.
%\item T. Zhang, J.G. W\"ohlbier, K. D. Choquette, N. Tabatabaie.
%  Microcavity Vacuum-Field Configuration and the Spontaneous Emission
%  Power. {\it IEEE Journal on Selected Topics in Quantum Electronics.}
%  Vol.~1, no.~2, pp.~601--605, 1995.
%  \\$\Rightarrow$8 citations.
%\end{enumerate}
%\clearpage



%{\bf\large Manuscripts in Preparation}

%{\bf\large Book Chapter}
%\begin{itemize}
%\item Section 3, ``Theoretical Principles,'' in Chapter 9,
%  ``How to Achieve Linear Amplification,'' in Barker, R.J., Booske,
%  J.H., Luhmannn, N.C., Nusinovich, G.S. (2005).
%  {\it Modern Microwave and Millimeter Wave Power Electronics:} IEEE
%  Press.
%\end{itemize}
%
%{\bf\large Software}
%\begin{itemize}
%\item J.G.~W\"ohlbier. LATTE/MUSE Numerical Suite ({\em lmsuite}).
%  A suite of 1-d nonlinear Traveling Wave Tube codes provided
%  to the microwave vacuum electronics community for research purposes.
%  Codes are used by several international researchers.
%  Available for download at {\tt http://www.lmsuite.org}
%\end{itemize}
%
%{\bf\large Computing Skills}
%\begin{itemize}
%\item Linux, Windows and Macintosh, parallel computer programming with
%  the Message Passing Interface (MPI), C++, C, Fortran, object oriented
%  programming in most modern languages.
%\end{itemize}

% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Python \cpshalf Swift \ \ \textbf{\emph{Familiar:}} \ \  Javascript \cpshalf Objective-C \cpshalf Bash \cpshalf Java \cpshalf Scheme}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{Programming Paradigms \cpshalf GIT \cpshalf CLI \cpshalf Agile Methodology \cpshalf DevOps Lifecycles}}
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Jupyter \cpshalf Matplotplib \cpshalf Numpy \cpshalf Pandas \cpshalf Scikit-learn \cpshalf Gym \cpshalf PyTorch \cpshalf Tensorflow}}
    %
    \newcommand{\skillfour}{\createskill{Performance
        Engineering}{Intel VTune \& Advisor \cpshalf Arm Forge
        \cpshalf TAU Commander}}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}

%{\bf\large Honors and Awards}
%\begin{itemize}
%\item 2003 Agnew National Security Postdoctoral Fellow, Los Alamos
%  National Laboratory. Highly competitive fellowship, only three
%  awarded out of nearly 400 post-docs.
%\item 1993 Teaching Assistant of the Year Award. University of
%  Wisconsin--Madison.
%  An award decided by student vote in the department of Electrical and
%  Computer Engineering.
%\end{itemize}
%
%{\bf\large Patent}
%\begin{itemize}
%\item U.S. Patent 6,087,916. Cooling of coaxial winding transformers in
%  high power applications. N.H. Kutkut, D.M. Divan, J.G. Wohlbier,
%  R.W. Gascoigne.
%\end{itemize}
%
%%\pagebreak
%%\input{files/conferences}
%
%%\input{files/theses}
%
%{\bf\large Professional Societies}
%\begin{itemize}
%\item Institute of Electrical and Electronics Engineers -- Member
%\item American Physical Society -- Member
%\end{itemize}

%{\bf\large Teaching Experience}
%\begin{itemize}
%\item Guest Lecturer, Electrical and Computer Engineering,
%  University of Wisconsin--Madison, 1998--2003.\\
%  Frequently lecture undergraduate electromagnetic theory courses.
%\item Teaching Assistant, Physics, University of Wisconsin--Madison,
%  1999.\\
%  Prepared and led discussion and laboratory sessions for
%  undergraduate Physics class in electromagnetism. Received highest
%  evaluation of all Teaching Assistants (9) in course.
%\item Teaching Assistant, Electrical and Computer Engineering,
%  University of Wisconsin--Madison, 1993--1994.\\
%  Developed and assisted advanced undergraduate
%  laboratories. TA of the year award.
%\end{itemize}

\createfootnote
\end{document}
