{\bf\large Conference Papers and Presentations}
\begin{itemize}
%\item S.R. Hudson {\it et al.} Influence of pressure-gradient and
%  shear on ballooning stability in stellarators.
%  20$^{\rm th}$ International Atomic Energy Agency Fusion Energy
%  Conference, November 2004.
\item J.G. W\"ohlbier, S. Sengele. New Eulerian methods for nonlinear
  wave equations: computing multi-valued solutions in a traveling wave
  tube. 46$^{\rm th}$ Annual Meeting of the American Physical Society
  Division of Plasma Physics, November 2004.
\item J.G. W\"ohlbier, C.C. Hegna. Finite Larmor radius stabilization
  of ideal ballooning instabilities in 3-d plasmas.
  Innovative Confinement Concepts Workshop, May 2004.
\item J.G. W\"ohlbier, J.H. Booske. A modal description of
  intermodulation injection in a klystron. Fifth IEEE International
  Vacuum Electronics Conference, April 2004.
\item A. Singh, J.E. Scharer, J.G. W\"ohlbier,
  J.H. Booske. Sensitivity of harmonic injection and its spatial
  evolution for nonlinear distortion suppression in a TWT.
  Fifth IEEE International Vacuum Electronics Conference, April 2004.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson, A. Singh,
  J.E. Scharer. A new look at the nonlinear physics of Traveling Wave
  Tubes. 45$^{\rm th}$ Annual Meeting of the American Physical Society
  Division of Plasma Physics, October 2003.
\item J.G. W\"ohlbier, C.C. Hegna. Finite Larmor radius stabilization
  of ideal ballooning modes in three-dimensional geometry.
  45$^{\rm th}$ Annual Meeting of the American Physical Society
  Division of Plasma Physics, October 2003.
\item C.C. Hegna, J.G. W\"ohlbier. Finite Larmor radius stabilization
  of ideal ballooning modes in three-dimensional geometry.
  14$^{\rm th}$ International Stellarator Workshop, September 2003.
\item S. Bhattacharjee {\it et al.} Folded waveguide traveling wave
  tube sources for THz radiation. 30$^{\rm th}$ International
  Conference on Plasma Science, June 2003.
\item A. Singh, J.G. W\"ohlbier, J.E. Scharer, J.H. Booske. Injection
  schemes for TWT linearization. 30$^{\rm th}$ International
  Conference on Plasma Science, June 2003.
\item J.G. W\"ohlbier, M.C. Converse, J. Plouin, A. Rawal, A. Singh,
 J.H. Booske. LATTE/MUSE numerical suite: an open source teaching and
 research code for traveling wave tube amplifiers. 30$^{\rm th}$
 International Conference on Plasma Science, June 2003.
\item S. Bhattacharjee {\it et al.} Investigations of folded waveguide
  TWT oscillators for THz radiation. Fourth IEEE International Vacuum
  Electronics Conference, May 2003.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson.
  The Physics of Phase Nonlinearity in a Traveling Wave Tube.
  44$^{\rm th}$ Annual Meeting of the American Physical Society
  Division of Plasma Physics, November 2002.
\item X. Li, J.G. W\"ohlbier, S. Jin, J.H. Booske.
  An Eulerian Method for Computing Multi-valued Solutions of the
  Euler-Poisson Equations.
  44$^{\rm th}$ Annual Meeting of the American Physical Society
  Division of Plasma Physics, November 2002.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson.
  Comparison of Transfer Curve Induced Distortions to Distortions in
  Nonlinear Physical TWT Models.
  28$^{\rm th}$ IEEE Conference on Plasma Science, June 2002.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson.
  The Physics of Harmonic Injection in a TWT.
  3$^{\rm rd}$ IEEE International Vacuum Electronics Conference, April
  2002.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson.
  Finite Bandwidth and Space Charge Effects in the MUSE Model. IEEE
  Pulsed Power Plasma Science Conference, June 2001.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson.
  New Nonlinear Multifrequency TWT Model.
  2$^{\rm nd}$ IEEE International Vacuum Electronics Conference, April 2001.
\item J.G. W\"ohlbier, I. Dobson, J.H. Booske.
  Four Multitoned Traveling Wave Tube Models.
  27$^{\rm th}$ IEEE Conference on Plasma Science, June 2000.
\item M.A. Wirth {\it et al.} Investigations of non-linear spectral
  behavior in multi-toned helix traveling wave tubes. 27$^{\rm th}$
  IEEE International Conference on Plasma Science, June 2000.
\item J.G. W\"ohlbier, J.H. Booske, I. Dobson.
  Comparison of Four Multifrequency Traveling Wave Tube Models.
  42$^{\rm nd}$ Annual Meeting of the American Physical Society Division
  of Plasma Physics combined with the 10$^{\rm th}$ International Congress
  on Plasma Physics, October 2000.
\item J.G. W\"ohlbier, I. Dobson, J.H. Booske, J.E. Scharer.
  Simplified Model of a Multitoned Traveling Wave Tube Amplifier.
  41$^{\rm st}$ Annual Meeting of the American Physical Society Division
  of Plasma Physics, November 1999.
\item J.G. W\"ohlbier, I. Dobson, J.H. Booske, J.E. Scharer.
  Simplified Model of a Multitoned Traveling Wave Tube Amplifier.
  26$^{\rm th}$ IEEE Conference on Plasma Science, June 1999.
\item J.G. W\"ohlbier, J.H. Booske, J.E. Scharer, I. Dobson, B. VanVeen.
  Characterization of Nonlinearities in Multitone Helix Traveling Wave Tube
  Amplifiers.
  40$^{\rm th}$ Annual Meeting of the American Physical Society Division
  of Plasma Physics, November 1998.
\end{itemize}
