{\noindent\bf Experience}

\begin{itemize}
\item {\bf High Performance Computing Consultant.} Performance engineering
for US Navy computational fluid dynamics codes. Application of performance
analysis tools including Allinea MAP, Open$|$SpeedShop, Scalasca, Score-p, TAU,
and Ravel to diagnose performance issues and implement solutions to improve
performance. Developed best practices guide for application of performance
engineering methodologies to scientific codes. Worked on performance
engineering of computational fluid dynamics miniapps on Intel Knight's
Landing processors.
\item {\bf Multi-physics software development for high performance
  computing.} Active on several multi-physics code projects for high
performance computing for 10 years. Physics include but are not
limited to compressible hydrodynamics, radiation-matter coupling, and
magnetohydrodynamics. Recent
activities include coding and optimization for Intel Xeon Phi
coprocessors and NVidia GPUs, and implementation of distributed memory
parallel domain decomposition and parallel
I/O for an unstructured tetrahedral mesh
code. C++/C/Fortran. MPI/OpenMP/OpenCL/CUDA. 
\item {\bf Project lead for ``Multi-physics on multi-core''.} Lead
  successful effort to develop multi-physics code for the Cell
  processor in the Roadrunner supercomputer era. Roadrunner was a
  radically different heterogeneous architecture that required
  simultaneous use of the three very different types of processors on
  the system. The compute engine on the Cell processor was a short
  vector processor similar to what is emerging in current Intel
  hardware, but had additional barriers to use such as the need to
  specifically issue direct memory accesses (DMA's) to load
  registers.
\item {\bf Data Science Consultant.} Consulted on several data science
  projects with data science company. Developed {\em R} based
  prediction models using large financial and demographic data
  sets. Name of data science company available upon request.
\item {\bf Post-doc and graduate student mentor.} Mentored two
  post-doctoral researchers, both of which are now productive and well
  respected staff scientists. Mentored and worked with several
  graduate students pursuing degrees in computational physics.
\end{itemize}